Generating Simulated Data

### 2021-05-24 docs/SimData.Rmd
first try observation diets in Gavin's format

@@

#multiple surveys named in list object, add to file
for(s in names(all_diets)){
  #arrange into long format: year, Species, agecl, length 
  svagelenbin <- len_comp_data[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%
    dplyr::left_join(modbins) %>%
    dplyr::filter(modbin.min < upper.bins & upper.bins <= modbin.max) %>%
    dplyr::group_by(species, year, agecl, sizebin) %>%
    dplyr::summarise(sumlen = sum(atoutput)) %>%
    dplyr::group_by(species, year, sizebin) %>%
    dplyr::mutate(propage = sumlen/sum(sumlen)) #proportion of each agecl contributing to lengthbin

  svdietprop <- all_diets[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time.days/365)) %>%
    # join with agecl to length lookup
    dplyr::select(species, agecl, year, prey, dietSamp) %>%
    dplyr::left_join(svagelenbin) %>%

    dplyr::filter(modbin.min < upper.bins & upper.bins <= modbin.max) %>%
    dplyr::group_by(species, year, sizebin) %>%
    dplyr::summarise(sumlen = sum(atoutput)) %>%
    tidyr::spread(sizebin, sumlen) %>%
    ungroup() %>%
    dplyr::mutate(inpN = rowSums(.[,-(1:2)], na.rm = TRUE)) %>%
    dplyr::mutate(type = 0) %>%
    dplyr::mutate(survey = s) %>%
    dplyr::mutate_at(vars(contains("sizebin")), ~./inpN) %>%
    dplyr::select(survey, year, species, type, inpN, everything())

>>>>

# get Dirichlet alphamults from config files
svcon <- list.files(path=here("/simulated-data/config/"), pattern = "*survey*", full.names = TRUE)

svalphamultlook <- tibble()
for(c in 1:length(svcon)){
  source(svcon[c])
  svalp <- tibble(
    surv_alphamult_n = alphamult, 
    survey = survey.name
  )
  svalphamultlook <- bind_rows(svalphamultlook, svalp)
}

@@

#multiple surveys named in list object
for(s in names(all_diets)){
  #arrange into lookup for agecl to lengthbin in numbers of fish 
  svagelenbin <- len_comp_data[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%
    dplyr::left_join(modbins) %>%
    dplyr::filter(modbin.min < upper.bins & upper.bins <= modbin.max) %>%
    dplyr::group_by(species, year, agecl, sizebin) %>%
    dplyr::summarise(sumlen = sum(atoutput)) %>%
    dplyr::group_by(species, year, sizebin) %>%
    dplyr::mutate(propage = sumlen/sum(sumlen)) #proportion of each agecl contributing to lengthbin

  svdietprop <- all_diets[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time.days/365)) %>%
    # join with agecl to length lookup
    dplyr::select(species, agecl, year, prey, dietSamp) %>%
    dplyr::left_join(svagelenbin) %>%
    dplyr::mutate(dietpropage = dietSamp*propage) %>% #reweight diets for lengthbins
    dplyr::group_by(species, year, sizebin, prey) %>%
    dplyr::summarise(dietsize = sum(dietpropage)) %>%
    dplyr::filter(prey %in% unique(modbins$species)) %>% #drops predators that don't eat our modeled species
    tidyr::spread(prey, dietsize) %>%
    ungroup() %>%
    dplyr::filter(!is.na(sizebin)) %>% 
    dplyr::mutate(allotherprey = 1-rowSums(.[,-(1:3)], na.rm = TRUE)) %>%
    dplyr::mutate(survey = s) %>%
    dplyr::left_join(svalphamultlook) %>% #what is effective sample size for Dirichlet?
    dplyr::rename(inpN = surv_alphamult_n) %>% #use this input for now
    dplyr::select(survey, year, species, sizebin, inpN, everything())

  allsvdietprop <- bind_rows(allsvdietprop, svdietprop)
}
write_csv(allsvdietprop, paste0(o.name,"observation_diets_NOBA_allsurvs.csv"))
